---
title: "Forecasting Project & Model Accuracy Comparison"
author: "Aleksej Hoffärber, Egor Zmaznev"
date: "3/4/2020"
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
# Libraries and theme----
library(fpp2)
library(ggplot2)
library(PerformanceAnalytics)
library(corrplot)
library(ggpubr)
library(seasonal)
library(splines)
library(dplyr)
library(magrittr)
library(readr)
library(skimr)
library(urca)
library(tsDyn)
library(ForecastComb)

theme_set(theme_minimal())

```

## Goals and Procedure

The aim of this short project was to investigate the behavior of statistical time-series models and their mathematical assumptions. Main subject of this study are ARIMA and SARIMA models that were used to understand the relationship between consumption and GDP in Australia.

Furthermore, the performance of the models was compared to ETS, TBATS, Average. DR+ARIMA etc. The results indicated, that DR+ETS approaches performed best considering the given data.

```{r preprocess, echo=FALSE, message=FALSE, warning=FALSE, results=FALSE}
df <- read_csv("data.csv")

df %<>% 
  filter(LOCATION == "AUS") %>% 
  select(SUBJECT, TIME, Value) %>%
  tidyr::spread(SUBJECT, Value) %>% # only calling single function to reduce conflicts between tidyr and dplyr
  rename(Date = TIME,
         di = B6NS1,
         ce = P3S1)

# creating time-series object
tse <- ts(df[,2:3], start = c(1959,3), end = c(2019,4), frequency = 4)

# binding date information from ts object to original df (easier than transforming the original format to a R date format)
df <- cbind(as.double(time(tse)), df) 
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
